A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
added abstract.

\begin{abstract}
Highly frequent in experimental tests related to data mining, the Adult Database
has some interesting properties which make it quite useful to test the 
efficiency of classification algorithms. This report aims to describe the Adult
Database from a statistical perspective and taking into account its support for
data mining tasks.
\end{abstract}

>>>>

\begin{abstract}
Classification is the process of predicting categorical labels in data. It has a
particular interest in a wide range of real world situations, where efficient
data analysis can provide a higher understanding of data at large. Taking that 
into account, the adult database, highly frequent in experimental tests related
to data mining, provides a solid data background to test different types of 
classification and to obtain interesting and relevant models to real world 
situations. This report aims to describe different approaches on building 
classifiers with the adult database and to conclude both on the accuracy of the
models built and on the properties obtained by them.
\end{abstract}
